Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-06-21 ms.tex
change name of dipole vs. spherical harmonic correction figure

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:quad} Summary of low-order corrections at 100 GHz.}
\end{center}
\end{figure*}

@@

We found that a dipole correction alone could not sufficiently rectify the 
\PLANCK~100 GHz map (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we 
performed a modified version of the Equation \ref{equ:dip} fit, using the 
following model:

@@

Where $Y_{l}^{m}$ are the real spherical harmonics, and the $a_{lm}$ are their 
corresponding real coefficients. The angle $\phi_p$ is taken simply to be 
$l_{gal, p}$ and $\theta_p$=$(90^{\circ}-b_{gal, p})$. Thus, we have replaced 
the Solar dipole term with a sum of 24 spherical harmonic templates, which, 
when multiplied by the best-fit $a_{lm}$ coefficients and subtracted from 
\PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
linear. Figure \ref{fig:quad} illustrates the improved correlation of 100 GHz 
vs. 857 GHz when including the spherical harmonic corrections relative to the 
dipole-only correction. The spherical harmonic decomposition of Equation 
\ref{equ:harm} did not improve the correlations at higher frequencies 
sufficiently to warrant replacing the dipole-only correction in those cases.

@@

In light of the \PLANCK~HFI data, it is possible to revisit the best-fit global
parameters of the two-component emission model. To derive the 
\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
maps, we employed a correlation slope analysis (see Figure XX). Specifically,
we correlated the observed \PLANCK~data against the appropriate FDS99 
prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
consideration due to the sensitivity of the 100 GHz trend to our ad hoc
low order corrections (see Figure \ref{fig:quad}). All comparisons between
\PLANCK~and the FDS99 predictions were made after smoothing both to 
$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
excellent.

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz.}
\end{center}
\end{figure*}

@@

We found that a dipole correction alone could not sufficiently rectify the 
\PLANCK~100 GHz map (see Figure \ref{fig:harm}). Therefore, for 100 GHz, we 
performed a modified version of the Equation \ref{equ:dip} fit, using the 
following model:

@@

Where $Y_{l}^{m}$ are the real spherical harmonics, and the $a_{lm}$ are their 
corresponding real coefficients. The angle $\phi_p$ is taken simply to be 
$l_{gal, p}$ and $\theta_p$=$(90^{\circ}-b_{gal, p})$. Thus, we have replaced 
the Solar dipole term with a sum of 24 spherical harmonic templates, which, 
when multiplied by the best-fit $a_{lm}$ coefficients and subtracted from 
\PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
linear. Figure \ref{fig:harm} illustrates the improved correlation of 100 GHz 
vs. 857 GHz when including the spherical harmonic corrections relative to the 
dipole-only correction. The spherical harmonic decomposition of Equation 
\ref{equ:harm} did not improve the correlations at higher frequencies 
sufficiently to warrant replacing the dipole-only correction in those cases.

@@

In light of the \PLANCK~HFI data, it is possible to revisit the best-fit global
parameters of the two-component emission model. To derive the 
\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
maps, we employed a correlation slope analysis (see Figure XX). Specifically,
we correlated the observed \PLANCK~data against the appropriate FDS99 
prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
consideration due to the sensitivity of the 100 GHz trend to our ad hoc
low order corrections (see Figure \ref{fig:harm}). All comparisons between
\PLANCK~and the FDS99 predictions were made after smoothing both to 
$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
excellent.
